Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-04-06 WSSSPE1_report/WSSSPE1_summary_report.tex
Introductory paragraph for Policy.

\todo{some text is needed here before the first subsection}

@@

The workshop submissions grouped under this section provide frameworks
for thinking about, researching and understanding which elements of sustainability
are important and how they relate. Although there is substantial
overlap between the frameworks, they have different emphases and
extents.  Each paper in this group included a definition of sustainability,
with many overlaps.  In essence the papers related the question to
change over time, an idea well captured in the definition used by the
UK's Scientific Software Sustainability Institute: ``software you use
today will be available---and continue to be improved and
supported---in the future,'' as quoted in~\cite{Venters_WSSSPE}. This
idea was also expressed as software that continues to serve its
users~\cite{Pierce_WSSSPE}.  A more thorough discussion of definitions
of software sustainability is presented in \S\ref{sec:defining-sustainability}.

>>>>

The Policy panel was designated to discuss the group of workshop
contributions dealing with the wide range of software sustainability
aspects that relate to establishing, promoting, and implementing
policies. Six papers presented frameworks for defining, modeling, and
evaluating software sustainability, the basis of establishing
policies. Four papers advocated mechanisms for more properly assessing
the impact of scientific software, and for crediting and recognizing
work that promotes software sustainability, all of which are
instrumental in effectively promoting policies that aim to change
current practices. Four papers discuss facets of implementing software
sustainability, and models of implementation across different facets.

@@

The workshop submissions grouped under this section provide frameworks
for thinking about, researching and understanding which elements of sustainability
are important and how they relate. Although there is substantial
overlap between the frameworks, they have different emphases and
extents.  Each paper in this group included a definition of sustainability,
with many overlaps.  In essence the papers related the question to
change over time, an idea well captured in the definition used by the
UK's Scientific Software Sustainability Institute: ``software you use
today will be available---and continue to be improved and
supported---in the future,'' as quoted in~\cite{Venters_WSSSPE}. This
idea was also expressed as software that continues to serve its
users~\cite{Pierce_WSSSPE}.  For a more thorough discussion of definitions
of software sustainability see \S\ref{sec:defining-sustainability}.
